Computing properties of independent sets by generic programming tensor networks \thanks{\funding{...}}

### 2022-01-05 paper/paper.tex
update fig5

\subsubsection{Number of independent sets and hard-square entropy constant}
In this examples, the types of graphs we used are shown in Figure~\ref{fig:lattices}, where vertices are all placed on square lattices with lattice dimensions $L \times L$.
The graphs include: the square grid graphs, denoted as SG; the square grid graphs with a filling factor $p$, denoted as SG$(p)$, where $\lfloor pL^{2} \rceil$ square grids are occupied with vertices;
the King's graphs, denoted as K; the King's graphs with a filling factor $p$, denoted as K$(p)$. 
The number of independent sets for square grid graphs of size $L \times L$ form a well-known integer sequence (\href{https://oeis.org/A006506}{OEIS A006506}), which is thought as a two-dimensional generalization of the Fibonacci numbers.
We computed the integer sequences for $L=38$ and $L=39$, which is not known before to our knowledge.
In the computation, we have used the finite field algebra trick for contracting arbitrarily high precision integer tensor networks.
We also computed the quantity $F(L,L)^{1/n}$ as a function of lattice size $L$ for these lattices,
where $F(L,L)$ is the number of independent sets of a given lattice size and $n$ is the number of vertices.
The results are shown in \Fig{fig:hardsquare}.

>>>>

\subsubsection{Number of independent sets and hard-square entropy constant}
In this examples, the types of graphs we used are shown in Figure~\ref{fig:lattices}, where vertices are all placed on square lattices with lattice dimensions $L \times L$.
The graphs include: the square grid graphs, denoted as SG; the square grid graphs with a filling factor $p$, denoted as SG$(p)$, where $\lfloor pL^{2} \rceil$ square grids are occupied with vertices;
the King's graphs, denoted as K; the King's graphs with a filling factor $p$, denoted as K$(p)$. 
The number of independent sets for square grid graphs of size $L \times L$ form a well-known integer sequence (\href{https://oeis.org/A006506}{OEIS A006506}), which is thought as a two-dimensional generalization of the Fibonacci numbers.
We computed the integer sequences for $L=38$ and $L=39$, which is not known before to our knowledge.
In the computation, we have used the finite field algebra trick for contracting arbitrarily high precision integer tensor networks.
We also computed the quantity $F(L,L)^{1/\lfloor pL^2\rceil}$ as a function of grid size $L$ for these lattices,
where $F(L,L)$ is the number of independent sets of a given grid size.
The results are shown in \Fig{fig:hardsquare}.
Our result for $p=1$ matches those in the literature, and the lattices with hole has much larger average value,
which has a phsical meaning of the hard lattices with holes have much larger mean entropy than those without holes at the high temperature limit.
